Equivalence Testing and the Second Generation P-Value

### 2018-08-16 sgpv_vs_TOST.Rmd
minor fix

lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
lines(p_tost_list, lwd = 3)
#abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
```
*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.

@@

tost_res2 <- TOSTone.raw(m = m, 
                   mu = mu,
                   sd = sd, 
                   n = n, 
                   low_eqbound = low_eqbound, 
                   high_eqbound = high_eqbound, 
                   alpha = alpha
)
SGPV2 <- TOST_to_SGPV(tost_res = tost_res2)
```
*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.

@@

```
*Figure 6*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis). Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.

@@

lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
lines(p_tost_list, lwd = 3)
abline(h = 0.5, 
       lty = 6,
       col = "lightgrey")
```
*Figure 9*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis). The sample size is small (n = 10), but because the sd is half as big as in Figure 7 (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4). The SGPV is not set to 0.5 (horizontal lightgrey line) but reaches a maximum slightly above 0.5 across a range of observed means.

@@

##The relation between equivalence tests and SGPV when confidence intervals are no symmetrical

>>>>

lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
lines(p_tost_list, lwd = 3)
#abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
```
*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.

@@

tost_res2 <- TOSTone.raw(m = m, 
                   mu = mu,
                   sd = sd, 
                   n = n, 
                   low_eqbound = low_eqbound, 
                   high_eqbound = high_eqbound, 
                   alpha = alpha
)
SGPV2 <- TOST_to_SGPV(tost_res = tost_res2)
```
*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.

@@

```
*Figure 6*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis). Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.

@@

lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
lines(p_tost_list, lwd = 3)
abline(h = 0.5, 
       lty = 6,
       col = "lightgrey")
```
*Figure 9*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of observed sample means (x-axis). The sample size is small (n = 10), but because the sd is half as big as in Figure 7 (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4). The SGPV is not set to 0.5 (horizontal lightgrey line) but reaches a maximum slightly above 0.5 across a range of observed means.

@@

##The relation between equivalence tests and SGPV when confidence intervals are not symmetrical
